State of the Practice of Lattice Boltzmann Method Software Development

### 2021-06-02 StateOfPractice/Peter-Notes/Report/Report.tex
edits to background section of LBM Report

Scientific computing software (SCS) is defined as the use of computer tools to analyze or simulate mathematical models of real world systems \citep{smith2006systematic}. Given the importance of such software, scientists and engineers desire methods and tools to sustainably develop high quality software, which has led to the formation of groups like the Software Sustainability Institute (\href{https://www.software.ac.uk/}{SEI}) and Better Scientific Software (\href{https://bssw.io/}{BSS}). The purpose of this state of the practice assessment is to understand how software quality in the LBM SCS family is impacted by software development choices, including principles, processes, and tools. A software family is defined
by \cite{parnas1976design} as “a set of programs whose common properties are so extensive that it is advantageous to study the common properties of the programs before analyzing individual members”. The common properties of the LBM family of related programs are listed in the a domain analysis in Section \ref{domainanalysis}. The software qualities that are assessed in this report are listed in Section \ref{softwarequalities}. Ensuring these qualities can take significant time, but as \cite{SmithEtAl2016} shows, SCS developers often cannot see themselves meeting the required time constraints to better develop some of the artifacts that improve software quality, like detailed documentation. Inability to develop such documentation due to time constraints could be mitigated by the use of automatic document generation tools like Drasil. The Drasil Framework consists of a collection of Domain Specific Languages (DSL) for capturing scientific documents, structures, and computing
knowledge, and then transforming this knowledge into relevant software artifacts without having to manually duplicate knowledge into multiple artifacts \citep{zhao2018}.

>>>>

SCS is defined as the use of computer tools to analyze or simulate mathematical models of real world systems \citep{smith2006systematic}. Given the importance of such software, scientists and engineers desire methods and tools to sustainably develop it with high quality. This has led to the formation of groups like the Software Sustainability Institute (\href{https://www.software.ac.uk/}{SEI}) and Better Scientific Software (\href{https://bssw.io/}{BSS}). The purpose of this state of the practice assessment is to understand how software quality in the LBM SCS family is impacted by software development choices, including principles, processes, and tools. A software family is defined
by \cite{parnas1976design} as “a set of programs whose common properties are so extensive that it is advantageous to study the common properties of the programs before analyzing individual members”. The common properties of the LBM family of related programs are listed as part of the domain analysis in Section \ref{domainanalysis}. The software qualities that are assessed in this report are listed in Section \ref{softwarequalities}. Ensuring software quality can take significant time, but as \cite{SmithEtAl2016} shows, SCS developers often cannot see themselves meeting the required time constraints to better develop some of the artifacts that improve qualities, like detailed documentation. An inability to develop such documentation due to time constraints could be mitigated by the use of automatic document generation tools like Drasil. The Drasil Framework consists of a collection of Domain Specific Languages (DSL) for capturing scientific documents, structures, and computing
knowledge, and then transforming this knowledge into relevant software artifacts without having to manually duplicate knowledge into multiple artifacts \citep{zhao2018}.
